A note on multi agent learning

### 2016-06-29 multiAgentLearning/paper/article.tex
added a fuckton of text

\todo{here we can interject an intermezzo, of how karandikar tried to solve
this with trajection and random perturbations}

\drafting Now consider a game versus tit for tat (TT), Tit for Tat is a
strategy that always copies the last action of its opponent.
This game can also be found in the \citep{stimpson:2001} paper:

@@

\section{A saticificing comparison}
\drafting So, until now we've seen thoroughly how saticificing play works, and even some
strengths and weaknesses. However,

\todo{
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

Finally some graphs are shown how they compare
}

>>>>

\toReview Now consider a game versus tit for tat (TT), Tit for Tat is a
strategy that always copies the last action of its opponent.
This game can also be found in the \citep{stimpson:2001} paper:

@@

\section{A saticificing comparison}
\drafting So, until now we've seen thoroughly how saticificing play works, and even some
strengths and weaknesses. However, what we really want to see is how it does
compare against other MAL algorithms. So to do this we'll first introduce the
competitors (Q-learning and WOLF-PHC) and then we'll show per game how they
do in comparison with help of the work of \citep{crandall}.

Q-Learning is described by \citep{sandholm} in the following way: ``The
Q-learning algorithm works by estimating the values of state-action pairs. The
value $Q(s,q)$ is the expected discounted sum of future payoffs obtained by taking
action $a$ from state $s$ and following an optimal policy thereafter.
Once these values have been learned, the optimal action from any state
is the one with the highest Q-value. After initializing the Q-values to arbitrary
numbers they are estimated based on experience as follows: 1. Select an action
$a$ from the current state $s$, causing an immediate payoff $r$ and arriving at
state $s'$. 2. Update $Q(s,a)$ based on this experience as follows:
\[\Delta Q(s,a) = \lambda[r+\gamma \text{ max }Q(s',b)-Q(s,a)]\]
Where $\lambda$ is the learning rate and $0 \leq \gamma < 1$ is the discount
factor.
3. Go to 1.
'' A look-up table is used to store the Q-values.

\todo{explain WOLF-PHC better?}
WoLF-PHC stands or win or learn fast policy hill climbing. It is 
introduced as an extension to q-learning. However with the addition that
learning rate should be increased when ``losing''. A more precise definition
can be found in the paper of \citep{bowling}.

The actual comparison of the algorithms is done by \citep{crandall}, in here
we will discuss several of his results. All the algorithms are compared in self
play. The first game result we'll discuss
is the already introduced prisoner's dillema:
\includegraphics[width=2.5in]{crandall/prisoners}

Where the S-Algorithm is saticificing play as defined by stimpson, WoLF-PHC is
defined as above and QL is Q-learning. We can clearly see saticificing play
performing a lot better than the other two algorithms in this instance.
(Note that in this figure different values were used than our example, but
the basic structure of the game is the same).

A game of chicken is a game where 2 players drive in a straight line in their
cars straight towards each other. If both players keep on driving straight,
they'll crash and get a bad reward. If one of them moves out of the way, he'll
be ashamed, but be better of than crashing, the other one will of course get
some fame, and if both players move out of the way, they'll share the same.
Formally it looks like this:

\begin{tabular}{lll}
              & Bend & Straight \\
    Bend & $(3,3)$     & $(2,3.5)$  \\
    Straight & $(3.5,2)$     & $(1,1)$  \\
\end{tabular}

And here is the result of Crandall:
\includegraphics[width=2.5in]{crandall/chicken}

In here we see again saticificing play performing better than Q-Learning and
WoLF. However, the difference is a lot less refined.

Shapley's game is a 3 action choice game. If saticificing play has to change
action, instead of picking the other action, it will just pick uniformly random
of the 2 other actions. The context of the game is left to the imagination
of the reader and the normal form game looks like this:

\begin{tabular}{llll}
              & a & b & c \\
    A & $(0,0)$ & $(0,1)$     & $(1.0)$  \\
    B & $(1,0)$ & $(0,0)$     & $(0.1)$  \\
    C & $(0,1)$ & $(1,0)$     & $(0.0)$  \\
\end{tabular}

This is the result of crandall:
\includegraphics[width=2.5in]{crandall/shapleys}

In here we can see saticifing play performing a lot worse than the other two
algorithms. This is because, Crandall explains, the joint aspiration never
falls below the Pareto frontier, thus the behavior is essentially random.
